% Test case 2. This should succeed.
% Test of the typesetting of examination questions
% and answers in left and right frames.

\input{meta/vsvhdr_integrated.tex}

This is an example of a fictional exam question.

\the\topskip

\the\partopsep

\the\topsep


\begin{vsvframe}{1-0:00}{1-5:00}{right}

\begin{enumerate}[(a)]
\vsvitem{}{1-0:10}{grey}
Here is a bit of code. Start by looking at it.

\begin{Verbatim}
public static bool isThisGrey() {
    if (text is grey) {
        return true;
    } otherwise {
        return false;
    }
}
\end{Verbatim}

Did that work?
\vsvmarks{2}

\begin{itemize}
\vsvitem{}{1-0:15}{grey}
Yes. Good.
\end{itemize}

\vsvitem{}{1-0:20}{grey}
Explain what is meant by source code, machine code and Java bytecode.
Give two advantages of distributing Java software as bytecode rather than source code.
\vsvmarks{5}

\begin{itemize}
\vsvitem{}{1-0:25}{grey}
\emph{Source code}:
High-level code written by a developer.
Can be understood and reasoned about by humans.
For most tasks, the developer does not need knowledge of the underlying architecture on which the code will be run.
\vsvitem{}{1-0:30}{grey}
\emph{Machine code}:
Low-level instructions that are decoded and executed by a processor.
Instructions are defined by that processor's instruction set and will differ between architectures.
Machine code is not usually read or written by humans except to perform extreme optimisations (e.g.\ scheduler in an operating system).
\vsvitem{}{1-0:35}{grey}
\emph{Java bytecode}:
Machine code for an abstract machine -- the Java Virtual Machine.
Stack-based architecture.
Small code size.
%\vsvitem{}{1-0:40}{grey} \emph{Advantages}:
%Cross-platform -- can be run on any architecutre for which a JVM has been written. Can be obfuscated to make reverse engineering hard -- easier to protect IP than if distributing the source code.
\end{itemize}
\end{enumerate}
\end{vsvframe}



\begin{vsvframe}{1-0:00}{1-5:00}{left}
Here's a state machine:

\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=2.5cm,
semithick]
\tikzstyle{every state}=[fill=white,draw,text=black, minimum width=1.2cm]
\node[state] (S0) {$S_0$};
\node[state] (S1) [right of = S0] {$S_1$};
\node[state] (S2) [right of = S1] {$S_2$};
\node[state] (S3) [right of = S2] {$S_3$};

\path (S0) edge node {$N$} (S1)
(S1) edge node {$N$} (S2)
(S2) edge node {$N+D$} (S3)
(S3) edge[loop below] node {$1$} (S3)
(S0) edge[bend left=60] node {$D$} (S2)
(S1) edge[bend right=60] node[below] {$D$} (S3)
(S0) edge[loop below] node {$\overline{D}.\overline{N}$} (S0)
(S1) edge[loop below] node {$\overline{D}.\overline{N}$} (S1)
(S2) edge[loop above] node {$\overline{D}.\overline{N}$} (S2)
;
\end{tikzpicture}

\end{vsvframe}

\input{meta/vsvftr.tex}
